### 2016-03-21 manuscript.Rnw
update 'traits' citation

As trait databases are becoming increasingly more common, and interfaces to the
data they contains are being developed as R packages \citep[e.g., the package
\texttt{traits}][]{Chamberlain2015}, \texttt{rotl} provides a way to easily
retrieve phylogenetic information for species trait data that are available.

>>>>

As trait databases are becoming increasingly more common, and interfaces to the
data they contains are being developed as R packages \citep[e.g., the package
\texttt{traits}][]{Chamberlain2016}, \texttt{rotl} provides a way to easily
retrieve phylogenetic information for species trait data that are available.
